---
title: "Alcohol vs Seat choice"
author: "Leah Castro"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

I noticed that the number of people sitting in the middle is the highest 89 between the number of people sitting in the front 40 and the back 36.
However, the standard deviation of the people sitting in the back is the highest 12.580471 compared to the people sitting in the front 3.806013 and the middle 6.22538.  

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

When looking at the P-value which was about 0.000116, I noticed that it is really small and tells me that there is a big statistical difference between the values.  

```{r}
plot(TukeyHSD(model1))
```

At the 95% confidence level, I examined the confidence intervals for the Front-Back, Middle-Back, and Middle-Front seats, with 0 representing no significant difference. The results show that the Front-Back and Middle-Back seats are significantly different, as 0 does not fall within their confidence intervals. In contrast, for the Middle-Front seats, 0 lies within the confidence interval, indicating no significant difference between them.

## Conclusions

In today’s lesson, I worked with numerical categorical data with multiple categories, using my helper file for the necessary numerical and inferential results. The numerical data showed the number of people in the front, middle, and back rows, with the middle row having the most at 89. I also calculated standard deviations, finding the back row had the highest at 12.58. The inferential results gave a very small P-value (0.000116), indicating significant differences. A 95% confidence interval chart showed that Front-Back and Middle-Back seats are significantly different, while 0 falls within the Middle-Front interval, indicating no significant difference there.
