---
title: "Alcohol vs Seat choice"
author: "Leah Castro"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

I noticed that the number of people sitting in the middle is the highest 89 between the number of people sitting in the front 40 and the back 36.
However, the standard deviation of the people sitting in the back is the highest 12.580471 compared to the people sitting in the front 3.806013 and the middle 6.22538.  

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

When looking at the P-value which was about 0.000116, I noticed that it is really small and tells me that there is a big statistical difference between the values.  

```{r}
plot(TukeyHSD(model1))
```

At the 95% confidence level, I examined the confidence intervals for the Front-Back, Middle-Back, and Middle-Front seats, with 0 representing no significant difference. The results show that the Front-Back and Middle-Back seats are significantly different, as 0 does not fall within their confidence intervals. In contrast, for the Middle-Front seats, 0 lies within the confidence interval, indicating no significant difference between them.

## Conclusions


